Tutorial_3

### 2024-09-17 Tutorial_3.Rmd
remove redundant models

```{r fit-model}
model_M3_freq <- glmer(event ~ 1 + condition*period_9 + 
                           condition*I(period_9^2) + 
                           condition*I(period_9^3) +
                           trial_c*period_9 + 
                           trial_c*I(period_9^2) + 
                           trial_c*I(period_9^3) +
                           (1 + condition*period_9 +
                           condition*I(period_9^2) +
                           condition*I(period_9^3) +
                           trial_c*period_9 + 
                           trial_c*I(period_9^2) + 
                           trial_c*I(period_9^3) | pid),

              # control parameters, data set, and complementary log-log link function
              control = glmerControl(optimizer = c("bobyqa", "Nelder_Mead"),
                                     optCtrl = list(maxfun=1000000)), 
              data=M3_data, 
              family=binomial(link="cloglog"))
```

3 hours...

```{r inspect-model}
summary(model_M3_freq)

model_M3 <- readRDS("Tutorial_2_Bayesian/models/model_M3.rds")

fixef(model_M3_freq)

coef(model_M3_f)

model_M3_f@beta

summary(model_M3_freq)

model_M3_freq@theta
model_M3_freq@u

model_M3_freq@flist

save(model_M3_freq, file="Tutorial_3_Frequentist/model_M3_freq.RData")

plot(1:16,fixef(model_M3_f),  ylim=c(-2,1), xaxis=NULL)
axis(1,at=1:16,labels=names(fixef(model_M3_f)),)
points(fixef(model_M3)[,1], col="red")
points(fixef(model_M3_fr), col="green")
points(fixef(model_M3_freq), col="blue")

length(names(fixef(model_M3_f)))
```

```{r fit-model}
model_M3_fr <- glmer(event ~ 1 + condition*period_9 + 
                           condition*I(period_9^2) + 
                           condition*I(period_9^3) +
                           trial_c*period_9 + 
                           trial_c*I(period_9^2) + 
                           trial_c*I(period_9^3) +
                           (1 + condition*period_9 +
                           condition*I(period_9^2) +
                           condition*I(period_9^3) +
                           trial_c*period_9 + 
                           trial_c*I(period_9^2) + 
                           trial_c*I(period_9^3) | pid),

              # control parameters, data set, and complementary log-log link function
              control = glmerControl(optimizer = c("nlminbwrap"),
                                     optCtrl = list(maxfun=1000000)), 
              data=M3_data, 
              family=binomial(link="cloglog"))
```

```{r save-model}
save(model_M3_fr, file="Tutorial_3_Frequentist/model_M3_fr.RData")
```

@@

>>>>

@@

Model_M3_f took about 3 hours.
